Investing in infants: the lasting effects of cash transfers to new families

### 2024-07-30 posts/BarrEgglestonSmith/BarrEgglestonSmith2022.qmd
Corrected bottom link to BarrEgglestonSmith2022.html

::: {.incremental}
* Students born in 1992-1999 (1993-98 recentred years)  
* Birth dates, academic achievements, behaioral records, free and reduced-price lunch (FRL) eligibility  
   * Income thresholds are similar between EITC and FRL  
      * \$25,600 (FRL) vs. \$27,400 (EITC) in 2000  
      * EITC eligible rate $\simeq$ 75% of all FRL eligible  
* Born within $\pm$0928 day windows of Jan 1 (excluding closest 8 days on both sides): 44,992 students  
:::

>>>>

::: {.incremental}
* Students born in 1992-1999 (1993-98 recentred years)  
* Birth dates, academic achievements, behaioral records, free and reduced-price lunch (FRL) eligibility  
   * Income thresholds are similar between EITC and FRL  
      * \$25,600 (FRL) vs. \$27,400 (EITC) in 2000  
      * EITC eligible rate $\simeq$ 75% of all FRL eligible  
* Born within $\pm$ 0928 day windows of Jan 1 (excluding closest 8 days on both sides): 44,992 students  
:::
